---
title: "CDRL Report- Lundh"
author: Anna Lundh
output: html_document
---

##This dataset includes data values gathered from a study on humans exploring the connection between height, weight, variables such as age and BMI, with hypertension. In this report, the relationship between BMI and systolic BP and between BMI and diastolic BP was explored graphically. The spread of the data, including the median, mean, minimum and maximum were used to understand the spread of the data values in this data set. The questions looked at in this report are, what is the relationship, if there is any, between BMI and systolic BP and between BMI and diastolic BP. Also, how do factors like age and gender relate to systolic BP and diastolic BP measurements.  

```{r }
summary(anna.dataset..1.)
```

## The plots of BMI vs. Systolic BP and BMI vs. Diastolic BP are shown below. The BMI is on the x-axis and systolic and diastolic were plotted on the y-axis. The plots show that there is a very weak increasing linear relationship between BMI and systolic BP and between BMI and diastolic BP. The linear model showing the relationship between weight and BMI showed a strong, increasing linear relationship between the two variables. 
```{r }
plot(systolic ~ bmi, anna.dataset..1.)
regrline <- lm(systolic ~ bmi, anna.dataset..1.)
abline(regrline, lwd=3, col='red')
summary(regrline)

plot(diastolic ~ bmi, anna.dataset..1.)
regrline <- lm(diastolic ~ bmi, anna.dataset..1.)
abline(regrline, lwd=3, col='red')
summary(regrline)

plot(bmi ~ weight, anna.dataset..1.)
regrline <- lm(bmi ~ weight, anna.dataset..1.)
abline(regrline, lwd=3, col='red')
summary(regrline)
```
## The conclusions that can be drawn from this data set are that there is a very weak, increasing linear relationship between BMI and systolic BP, as well as between BMI and diastolic BP. There is a strong, increasing linear relationship between weight and BMI. 
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
